Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-01-26 apples_and_oranges.qmd
Calculated change scores using percentage transformed variables

#Plot cohens d per arm

@@

#Plot percentage  baseline means

ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
  geom_point(position = position_jitter(width = 0.2), size = 3) +
  scale_color_manual(values = group_colors) +
  labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
  theme_minimal() +
  theme(legend.position = "none")

>>>>

# Plot cohens d per arm

@@

# Now look at change scores of percentage transformed variables

df_long_for_metan <- df_long_for_metan %>% 
  mutate(perc_change = perc_post_mean - perc_baseline_mean)

ggplot(df_long_for_metan, aes(x = group, y = perc_change, color = group)) +
  geom_point(position = position_jitter(width = 0.2), size = 3) +
  geom_segment(x = 4.5, xend = 4.5, y = -0.3, yend = -0.25, 
               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
  geom_text(x = "Psychotherapy Control", y = -0.3, label = "Less Effective", color = "grey", vjust = 0, hjust = .3) +
  geom_segment(x = 4.5, xend = 4.5, y = -0.4, yend = -0.45, 
               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
  geom_text(x = "Psychotherapy Control", y = -0.4, label = "More Effective", color = "grey", vjust = 0, hjust = .3) +
  scale_color_manual(values = group_colors) +
  labs(title = "Scatter plot of change scores (percentage transformed) by group", x = NULL, y = "Change") +
  theme_minimal() +
  theme(legend.position = "none")

# # Plot percentage  baseline means 
# 
# ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
#   geom_point(position = position_jitter(width = 0.2), size = 3) +
#   scale_color_manual(values = group_colors) +
#   labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
#   theme_minimal() +
#   theme(legend.position = "none")
